Legacy Data Confounds Genomics Studies

### 2019-05-02 LatexManuscript/legacy.tex
reordering of a few lines

%We apply the 1kGP strict mask after FDR-adjustments to allow the method to identify problematic regions already flagged as such.
There are 9,124 $Q$-associated variants that are within the flagged regions of the 1kGP strict mask. \sgcomment{Inconsistent?}
Lists of $Q$-associated variants and individuals with low $Q$ are provided in Supplementary Data.

$Q$-associated variants are distributed across the genome, with chromosome 1 showing an excess of such variants, and other chromosomes being relatively uniform (Figure \ref{CountPerChrom}).
At a 10kb scale, we also see rather uniform distribution with a small number of regions showing an enrichment for such variants (Figure \ref{VariantDensity}).
An outlying 10kb region in chromosome 17 \sgcomment{give coordinates} has 35 $Q$-associated variants.

Distribution of association statistics in this region is provided in Figure \ref{Top10}.

>>>>

%We apply the 1kGP strict mask after FDR-adjustments to allow the method to identify problematic regions already flagged as such.
Lists of $Q$-associated variants and individuals with low $Q$ are provided in Supplementary Data.

$Q$-associated variants are distributed across the genome, with chromosome 1 showing an excess of such variants, and other chromosomes being relatively uniform (Figure \ref{CountPerChrom}).
At a 10kb scale, we also see rather uniform distribution with a small number of regions showing an enrichment for such variants (Figure \ref{VariantDensity}).
An outlying 10kb region in chromosome 17 \sgcomment{give coordinates} has 35 $Q$-associated variants.
Distribution of association statistics in this region is provided in Figure \ref{Top10}.
By contrast, variants that do not pass the 1kGP strict mask are more unevenly distributed across the genome(Figure \ref{VariantDensity}).
